geozoo

### 2020-06-24 source/geozoo.Rmd
animated searching space exploration for noisy function example

library(tidyverse)
library(geozoo)

@@

@@

interp <- pca$combined %>% filter(info == "interpolation") %>% dplyr::select(V1:V5) %>% as.matrix()

a <- sphere.hollow(p = 5, n = 1000)
a$points <- a$points %>% rbind(interp)
color <- c(rep("black", 1000), rep("red", nrow(interp)))
print(a, col = color)
```

>>>>

library(tidyverse)
library(geozoo)
library(ferrn)

@@

```{r}
vis <- function(data, color = NULL, ...){

  row <- data$basis[[1]] %>% nrow()
  col <- data$basis[[1]] %>% ncol()
  dim <- row * col

  path <- data %>% pull(basis) %>% purrr::flatten_dbl() %>% matrix(ncol = dim, byrow = TRUE)

  a <- sphere.hollow(p = dim, n = 1000)
  a$points <- a$points %>% rbind(path)

  if(is.null(color)){
    color <- c(rep("grey", 1000), rep("red", nrow(data) - 1), "green")
  }

  print(a, col = color)

}
```

1. 1D projection using search_geodesic

- The final projection is colored green, with rotation, it is always posed on the opposite direction of V2 with same magnitude.

```{r}
# final basis 
holes_1d_geo %>% filter(info == "interpolation") %>% tail(1) %>% pull(basis)
# final basis after polish
holes_1d_geo_polish %>% tail(1) %>% pull(basis)

dt <- holes_1d_geo %>% filter(info == "interpolation")
color <-  c(rep("grey", 1000), rep("red", nrow(dt) - 1), "green")
vis(dt, color = color)

interp <- holes_1d_geo %>% filter(info == "interpolation")
polish <- holes_1d_geo_polish %>% filter(info == "loop_best")
dt_bind <- bind_rows(interp,polish)

color <- c(rep("grey", 1000), rep("red", nrow(interp) - 1),"green", rep("blue", nrow(polish)))
vis(dt_bind, color = color)

2. Comparing two search better paths

```{r}
# a small example 
interp1 %>% tail(1) %>% pull(basis)
interp2 %>% tail(1) %>% pull(basis)

# different seeds lead to different variables found
interp1 <- kol_cdf_1d_2var_better %>% filter(info == "interpolation")
interp2 <- kol_cdf_1d_2var_better_2 %>% filter(info == "interpolation")
dt_bind <- bind_rows(interp1, interp2)

color_hex <- RColorBrewer::brewer.pal(4, "Dark2")
color <- c(rep("grey", 1000), 
           rep(color_hex[[1]], nrow(interp1)-1), color_hex[[3]],
           rep(color_hex[[2]], nrow(interp2)-1), color_hex[[3]])

vis(dt_bind, color)
```

```{r}
# better random finds global

# explore the full parameter space 
interp1 <- kol_cdf_1d_2var_better %>% filter(info == "interpolation")
interp2 <- kol_cdf_1d_2var_better_2 %>% filter(info == "interpolation")
interp3 <- kol_cdf_1d_2var_better_random %>% filter(info == "interpolation")

polish1 <- kol_cdf_1d_2var_better_polish %>% filter(info == "polish_best")
polish2 <- kol_cdf_1d_2var_better_2_polish %>% filter(info == "polish_best")
polish3 <- kol_cdf_1d_2var_better_random_polish %>% filter(info == "polish_best")

dt_bind <- bind_rows(interp1, polish1, 
                     interp2, polish2,
                     interp3, polish3)

color_hex <- RColorBrewer::brewer.pal(8, "Dark2")
color <- c(rep("grey", 1000), 
           rep(color_hex[[1]], nrow(interp1) + nrow(polish1)-1), "green",
           rep(color_hex[[2]], nrow(interp2) + nrow(polish2)-1), "green",
           rep(color_hex[[3]], nrow(interp3) + nrow(polish3)-1), "green"
           )

vis(dt_bind, color)

# explore the reduced 2D space via PCAs
interp1 <- kol_cdf_1d_2var_better 
interp2 <- kol_cdf_1d_2var_better_2
interp3 <- kol_cdf_1d_2var_better_random

pca <- bind_rows(interp1, interp2, interp3) %>% 
  mutate(algorithm = c(rep("better1", nrow(interp1)), 
                       rep("better2", nrow(interp2)), 
                       rep("better_random", nrow(interp3)))) %>% 
  ferrn::compute_pca()

pca$combined %>% 
  ggplot(aes(x = PC1, y = PC2, color = algorithm)) + 
  geom_point() + 
  theme(aspect.ratio = 1)

interp3 %>% filter(tries > 40) %>% explore_trace_search()
interp3 %>% explore_trace_search()
```

```{r}
# finds V8
holes_2d_better %>% filter(info == "interpolation") %>% tail(1) %>% pull(basis)
# finds V3 and V8
holes_2d_better_max_tries %>% filter(info == "interpolation")%>% tail(1) %>% pull(basis)

interp1 <- holes_2d_better %>% filter(info == "interpolation")
polish1 <- holes_2d_better_polish %>% filter(info == "polish_best")
interp2 <- holes_2d_better_max_tries %>% filter(info == "interpolation")
polish2 <- holes_2d_better_max_tries_polish %>% filter(info == "polish_best")
dt_bind <- bind_rows(interp1, 
                     polish1, 
                     interp2, 
                     polish2
                     )

color_hex <- scales::brewer_pal(palette = "Dark2")(8)
scales::show_col(color_hex)
# color <- c(rep("grey", 1000), 
#            rep(color_hex[1], nrow(interp1)-1), color_hex[2], rep(color_hex[3], nrow(polish1)-1), color_hex[4],
#            rep(color_hex[5], nrow(interp2)-1), color_hex[6], rep(color_hex[7], nrow(polish2)-1), color_hex[8]
#            )

color <- c(rep("grey", 1000), 
           rep(color_hex[1], nrow(interp1)-1), "green", rep("red", nrow(polish1)-1), "blue",
           rep(color_hex[5], nrow(interp2)-1), "green", rep("lightblue", nrow(polish2)-1), "blue"
           )

dt_bind <- bind_rows(interp2, polish2)
color <- c(rep("grey", 1000), 
           rep(color_hex[1], nrow(interp2)), rep("red", nrow(polish2)-1), "blue")
vis(dt_bind, color)

@@

interp <- pca$combined %>% dplyr::select(V1:V5) %>% as.matrix()

a <- sphere.hollow(p = 5, n = 1000)
a$points <- a$points %>% rbind(interp)
color <- c(rep("black", 1000), "green",rep("red", nrow(interp)-1))
print(a, col = color)
```

$\mathcal{S}_{p-1}$ minus one because
